A Real-Time Sonar Simulator for Automatic Target Recognition

### 2016-07-28 Simulator/article.tex
la2pdf commit - 2016:07:28	12:02:03	(to.28.juli)

We have tested the template matching techniqiues on experimental data from the HISAS1030 synthetic aperture sonar (SAS) attached to the HUGIN autonomous underwater vehicle (AUV), both developed by Kongsberg Maritime. Three objects from Jesusbukta (Jesus Bay) in Norway will be presented; two roughly 3\,m long cylinders imaged a couple days apart in Janyary 2009, and a roughly 5\m long torpedo imaged in June 2012.

>>>>

We have tested the template matching techniqiues on experimental data from the HISAS1030 synthetic aperture sonar (SAS) attached to the HUGIN autonomous underwater vehicle (AUV), both developed by Kongsberg Maritime. Three objects from Jesusbukta (Jesus Bay) in Norway will be presented; two roughly 3\,m long cylinders imaged a couple days apart in Janyary 2009, and a roughly 5\,m long torpedo imaged in June 2012.
